Algebraic File Synchronization: Adequacy and Completeness

### 2016-10-15 p2/algebra.tex
Improved notation

In a more complete algebra from which the correctness and completeness
of reconciliation could also be derived,
one can also include symbols, inference rules and axioms for 
$\works{\seqset{A}}$ and $\worksc{\seqset{A}}{\seqset{B}}$.
We see proving the soundness and completeness of this extended algebra
an intriguing problem that is worthy of further research.

>>>>

In a more complete algebra from which the correctness and completeness
of reconciliation could also be derived,
one can also include symbols, inference rules and axioms for 
$\worksmnil{\seqset{A}}$ and $\worksm{\seqset{A}}{\seqset{B}}$.
We see proving the soundness and completeness of this extended algebra
an intriguing problem that is worthy of further research.

### 2016-10-15 p2/axioms.tex
Rewrote proof for new notation
Improved notation

So that we can describe the effects of commands in general,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we will investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
% For example, we will write
% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
Sequences of commands form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mydef}[$\eqext$]
% Relation in the algebra
$A\eqext B$ means that $B$ \emph{extends} $A$,
% intended interpretation:
that is, they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
% preorder: reflexive and transitive
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

@@

@@

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]\label{def_indep}
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they commute and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
\end{mydef}

@@

If $n=m$, then from \cref{ax_same_breaks} we know $[y]=[z]$ and $[w]=[x]$
as otherwise the commands, in one order or the other, would break all filesystems
and they could not be independent.
The commands are not assertion commands, so from \cref{ax_same_singlec}
we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
Therefore $[x]=[y]=[z]=[w]$ which with $y=w$ contradicts our assumption that the commands are different.

>>>>

% Sequences
% ---------

So that we can describe the effects of commands in general,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we will investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
% For example, we will write
% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
We write $\sets$ for the set of sequences of commands.
They form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mydef}[$\eqext$]
% Relation in the algebra
$A\eqext B$ means that $B$ \emph{extends} $A$,
% intended interpretation:
that is, they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
% preorder: reflexive and transitive
% patial order: reflexive, transitive and antisymmetric (aRb & bRa => a=b) TODO
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

@@

% TODO Rewrite script for new notation

@@

\begin{mydef}[$A\indep B$: Independent commands, sequences and sets]\label{def_indep}
Two commands $\cxynv$ and $\czwmv$ 
are independent, and we write $\cxynv\indep\czwmv$ if 
they commute and do not break all filesystems:
\[ \cxynv\cc\czwmv \equiv \czwnv\cc\cxynv \nequiv \cbrk. \]
For two sequences or unordered sets of commands $A$ and $B$ we write $A\indep B$ if
for all $\alpha$ in $A$ and all $\beta$ in $B$, $\alpha\indep\beta$.
We also write $\alpha\indep B$ iff $\forall \beta\in B:\alpha\indep\beta$.
\end{mydef}

@@

If $n=m$, then from \cref{ax_same_breaks} we know $[y]=[z]$ and $[w]=[x]$
as otherwise the commands, in one order or the other, would break all filesystems
and they could not be independent.
The commands are not assertion commands, so from \cref{ax_same_singlec}
we know that $\cxynv\cc\czwnv\equiv\czwnv\cc\cxynv$ can only happen if $y=w$.
% TODO Does this depend on |Vd|=1?
Therefore $[x]=[y]=[z]=[w]$ which with $y=w$ contradicts our assumption that the commands are different.

### 2016-10-15 p2/conclusion.tex
Improved notation

And finally, we hope that this work, together with \cite{NREC}, provides
a blueprint of constructing an algebra of commands for different storage protocols
(e.g. XML trees, mailbox folders, generic relational databases, etc.),
and of demonstrating the adequacy and completeness of update and conflict detection and reconciliation
algorithms defined over it.
This, in turn, can offer formal verification of the algorithms underlying
specific implementations in a variety of synchronizers.
Alternatively, by generalizing the parent--child relationships between filesystem nodes,
the demonstrated properties of minimal sequences of commands
and conditional operation of sequences ($\workssign$)
may also contribute to future research into algebraic structures
constrained by predefined sparse connections between their elements.

>>>>

And finally, we hope that this work, together with \cite{NREC}, provides
a blueprint of constructing an algebra of commands for different storage protocols
(e.g. XML trees, mailbox folders, generic relational databases, etc.),
and of demonstrating the adequacy and completeness of update and conflict detection and reconciliation
algorithms defined over it.
This, in turn, can offer formal verification of the algorithms underlying
specific implementations in a variety of synchronizers.
Alternatively, by generalizing the parent--child relationships between filesystem nodes,
the demonstrated properties of minimal sequences of commands
and conditional operation of sequences ($\worksmsign$) % TODO
may also contribute to future research into algebraic structures
constrained by predefined sparse connections between their elements.

### 2016-10-15 p2/rec-sound.tex
Minor updates
Improved notation

\begin{myth}
If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$,
where, to restate \cref{def:reconciliation},
% { % scope
% \renewcommand{\themydef}{\ref{def:reconciliation}}
% \begin{mydef}
\begin{align*}
\reca = \{\alpha|{}& \\
& \alpha\in A\setminus B \\
& \wedge \\
& \forall \beta\in B\setminus A: \alpha\indep\beta\\
\}. &
\end{align*}
% \end{mydef}
% } % scope
\end{myth}

This is trivial unless $\works{A,B}$, so we assume that it is true.
Let us first investigate the part of $A$ and $B$ that is excluded from
$\reca$: their intersection.

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
Then their intersection, in some suitable order, also works on any filesystem
either of them works on:
$\worksc{\acbnp}{A}$, and, by symmetry,
$\worksc{\acbnp}{B}$.
\end{mylem}

@@

Let us consider therefore the marked command preceded by an unmarked command in $A$,
and let the marked command be $\cxynv$, 
and the preceding unmarked command be $\czwmv$:
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots
\end{gather*}
As $A$ is simple and $\works{A}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $A$,
and we show that the last two cases are impossible as they would lead to contradiction.

@@

As $\works{A,B}$ and so $\works{A,B'}$, 
from \cref{worksinputmatch}
we know that $Q=Z$.

Going back to the construction and destruction pairs we see that the output type of the first command
is always the same, and it is either $\cchard$ or $\ccharb$ depending on the relationship between $n$ and $m$.
Therefore $R=W$ and $\cqrmv=\czwmv$
as $|\setd|=|\setb|=1$. 
If $B$ originally had a command on $m$,
this is a contradiction as $\czwmv$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
If $B$ had no command on $m$,
this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $Z=Q=R=W$, 
but $A$ contained no assertion commands.

We now know that there is an $A'\equiv A$ in which commands in $\acbnp$
are at the beginning, and therefore 
from \cref{worksextpostfix} we know that
$\worksc{\acbnp}{A}$ and by symmetry $\worksc{\acbnp}{B}$.
\end{proof}

@@

\noindent
We would like to prove that $\worksc{B\cc \reca}{A,B}$.
From the above we know that we can move commands in $\acbnp$
to the beginning of $B$ and so this is equivalent to
\[ \worksc{\acb\cc \bma\cc \reca}{A,B}. \]
As we already know that $\reca\indep\bma$
and that $\worksc{\acb\cc \bma}{A,B}$
(as $\worksc{B}{A,B}$),
we can prove our theorem based on \cref{indep_prefix_combine}
if we can prove that
\[ \worksc{\acb\cc \reca}{A,B}. \]
Using \cref{r_invmove} we can rephrase this as
\[ \worksc{\reca}{\acbi\cc A,\acbi\cc B}. \]

To restate some results above, we therefore already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
\item $\worksc{\amb, \bma}{\acbi\cc A,\acbi\cc B}$ 
because of \cref{r_invmove}
as $\worksc{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
\end{itemize}

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\ambnp$ to $S$ and $\bmanp$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksc{S,T}{\seqset{C}}$ for some set of sequences $\seqset{C}$,
   \end{itemize}
then
\[ \worksc{S^*}{\seqset{C}}. \]
\end{mylem}

\begin{proof}
This is trivial unless $\works{\seqset{C}}$, so we will assume that it is true
and therefore $\works{S,T}$.

The proof is similar to that of \cref{can_move_intersection}.
We mark all commands in $S$ that are in its subset $S^*$, and
we prove that $S$ can be transformed into $S'$ via equivalences
so that all marked commands would be at its beginning.
If so, then 
$\worksc{S^*}{\seqset{C}}$ 
based on \cref{worksextpostfix}
as $\worksc{S'}{\seqset{C}}$ and $S'=S^*\cc S_0$ 
where $S_0$ contains the remaining (conflicting) commands.

@@

Let therefore the marked command in $S$ be $\cxynv$
and the preceding unmarked command be $\czwmv$.
As $S$ is simple and $\works{S}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $S$,
and we show that the other two cases are not possible as they would lead to a contradiction.

>>>>

\begin{myth}
If $A, B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
\end{myth}

This is trivial unless $\worksmnilb{A,B}$, so we assume that it is true.
Let us first investigate the part of $A$ and $B$ that is excluded from
$\reca$: their intersection.

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
Then their intersection, in some suitable order, also works on any filesystem
either of them works on:
$\worksm{A}{\acbnp}$, and, by symmetry,
$\worksm{B}{\acbnp}$.
\end{mylem}

@@

Let us consider therefore the marked command preceded by an unmarked command in $A$,
and let the marked command be $\cxynv$, 
and the preceding unmarked command be $\czwmv$:
\begin{gather*}
A = \cdots\cc  \czwmv\cc  \cxynv\cc  \cdots
\end{gather*}
As $A$ is simple and $\worksmnilb{A}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $A$,
and we show that the last two cases are impossible as they would lead to contradiction.

@@

As $\worksmnilb{A,B}$ and so $\worksmnilb{A,B'}$, 
from \cref{worksinputmatch}
we know that $[q]=[z]$.

Going back to the construction and destruction pairs we see that the output value of the first command
is either $\vald$ or $\empt$ and is determined by the relationship between $n$ and $m$.
Therefore $r=w$ and $\cqrmv=\czwmv$.
If $B$ originally had a command on $m$,
this is a contradiction as $\czwmv$ was not marked, but we see it must also be in $B'$ and therefore in $B$.
If $B$ had no command on $m$,
this is a contradiction because the command on $m$ in $B'$ is an assertion command, so $[z]=[q]=[r]=[w]$, 
but $A$ contained no assertion commands.

We now know that there is an $A'\equiv A$ in which commands in $\acbnp$
are at the beginning, and therefore 
from \cref{worksextpostfix} we know that
$\worksm{A}{\acbnp}$ and by symmetry $\worksm{B}{\acbnp}$.
\end{proof}

@@

\noindent
We would like to prove that $\worksmbb{A,B}{B\cc \reca}$.
From the above we know that we can move commands in $\acbnp$
to the beginning of $B$ and so this is equivalent to
\[ \worksmbb{A,B}{\acb\cc \bma\cc \reca}. \]
As we already know that $\reca\indep\bma$
and that $\worksmbb{A,B}{\acb\cc \bma}$
(as $\worksmbb{A,B}{B}$),
we can prove our theorem based on \cref{indep_prefix_combine}
if we can prove that
\[ \worksmbb{A,B}{\acb\cc \reca}. \]
Based on \cref{r_invmove} and \cref{repr_works_is_same}, and because
we already know that $\worksmbb{A,B}{\acbnp}$,
this is equivalent to
\[ \worksmbb{\acbi\cc A\T,\acbi\cc B\T}{\reca\T}. \]

To restate some results above, we therefore already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
\item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
\item $\worksmbb{\acbi\cc A,\acbi\cc B}{\amb, \bma}$ 
because of \cref{r_invmove}
as $\worksmbb{A,B}{A,B}$,
and $A\equiv\acb\cc\amb$, and $B\equiv\acb\cc\bma$.
\end{itemize}

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\ambnp$ to $S$ and $\bmanp$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksmxb{\sqs{C}}{S^*}. \]
\end{mylem}

\begin{proof}
This is trivial unless $\worksmnil{\sqs{C}}$, so we will assume that it is true
and therefore $\worksmnilb{S,T}$.

The proof is similar to that of \cref{can_move_intersection}.
We mark all commands in $S$ that are in its subset $S^*$, and
we prove that $S$ can be transformed into $S'$ via equivalences
so that all marked commands would be at its beginning.
If so, then 
$\worksmxb{\sqs{C}}{S^*}$ 
based on \cref{worksextpostfix}
as $\worksmxb{\sqs{C}}{S'}$ and $S'=S^*\cc S_0$ 
where $S_0$ contains the remaining (conflicting) commands.

@@

Let therefore the marked command in $S$ be $\cxynv$
and the preceding unmarked command be $\czwmv$.
As $S$ is simple and $\worksmnilb{S}$, from 
\cref{ax_distantrel_breaks,ax_directchild_breaks,ax_directparent_breaks}
we know that these commands can only be on incomparable nodes or form a construction or destruction pair.
In the first case, swapping the commands results in a sequence equivalent to $S$,
and we show that the other two cases are not possible as they would lead to a contradiction.

### 2016-10-15 p2/upd-def.tex
New notation for commands
Improved notation

A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
that changes between the two states of the filesystem. Also, it is easy to see that this is also
sufficient, as there are commands available for any input and output value. 
Specifically, if at node $n$, $\FS(n)=\valvx$ and $\FS_A(n)=\valvy\neq \valvx$, then we add the command $\cxyaa{n}{\valvy}$ to $A$
where $\valvx\in\setvx{X}$ and $\valvy\in\setvx{Y}$.

@@

\begin{mydef}[Minimal set or sequence]
A sequence or set of commands is minimal if it contains at most one command on each node.
\end{mydef}

\begin{mydef}[Simple set or sequence]
A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
\end{mydef}

>>>>

A sequence that transforms $\FS$ into $\FS_A$ must contain at least one command on each node
that changes between the two states of the filesystem. Also, it is easy to see that this is also
sufficient, as there are commands available for any input and output value. 
Specifically, if at node $n$, $\FS(n)=x$ and $\FS_A(n)=y\neq x$, then we add the command $\cxyaa{n}$ to $A$.

@@

\begin{mydef}[Minimal sets or sequences, $\setsmin$]
A sequence or set of commands is minimal if it contains at most one command on each node.
We write $\setsmin$ for the set of minimal sequences.
\end{mydef}

\begin{mydef}[Simple sets or sequences, $\setssmp$]
A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
We write $\setssmp$ for the set of simple sequences.
\end{mydef}

### 2016-10-15 p2/works-inverse.tex
Improved notation

\begin{mydef}[Sets of sequences]
As we will frequently refer to sets of fequences,
we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
to denote such sets for brevity.
We will use $A\cc\sqs{B}$ to denote the set of sequences $\{A\cc B|B\in\sqs{B}\}$,
and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
\end{mydef}

@@

\begin{mycor}\label{workschained}
% An inference rule in the algebra
$\worksmeqsign$ can be chained:
if $\sqs{B'}\subseteq\sqs{B}$, then
$\worksm{\sqs{A}}{\sqs{B}} \wedge \worksm{\sqs{B'}}{\sqs{C}} \Rightarrow \worksm{\sqs{A}}{\sqs{B}\cup\sqs{C}}$.
\end{mycor}

@@

\begin{mydef}[$\T$]
We use $\T$ and write $a\T$ to denote the canonical mapping of 
values, filesystems, commands and sequences to the
representatives of their $\typeeq$-equivalence class.
\begin{itemize}
\item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
\item For commands, $\cbrk\T=\cbrk$ and $\cxynv\T = \cTxynv$.
\item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T | S\in\sqs{A}\}$.
\end{itemize}
\end{mydef}

@@

From the definitions we can clearly see that
\begin{mycor}\label{negneg_is_typeeq}
$\forall S: ({S\T}^{-1})^{-1} = S\T$.
\end{mycor}

@@

\begin{mylem}\label{indep_prefix_combine}
The combination of sequences with a common head and independent tails 
continues to work under the same conditions:
\[ \worksc{A\cc B}{\sqs{S}} \wedge \worksc{A\cc C}{\sqs{S}} \wedge B\indep C \Rightarrow \worksc{A\cc B\cc C}{\sqs{S}} \]
\end{mylem}
\begin{proof}
Based on \cref{repr_works_is_same} we have
$\worksc{A\T\cc B\T}{\sqs{S\T}}$ and $\worksc{A\T\cc C\T}{\sqs{S\T}}$,
and from \cref{r_invmove} we know
$\worksc{B\T}{{A\T}^{-1}\cc \sqs{S\T}}$ and $\worksc{C\T}{{A\T}^{-1}\cc \sqs{S\T}}$.
Using \cref{combine_independent_sequences} we get
$\worksc{B\T\cc C\T}{B\T,C\T}$,
and combining these using \cref{workschained}
we get
$\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \sqs{S\T}}$.

From $\worksc{A\cc B}{\sqs{S}}$ we also know $\worksc{A}{\sqs{S}}$ and $\worksc{A\T}{\sqs{S\T}}$.
We can combine this and $\worksc{B\T\cc C\T}{{A\T}^{-1}\cc \sqs{S\T}}$ using
the second proposition of \cref{r_invmove} to get
$\worksc{A\T\cc B\T\cc C\T}{\sqs{S\T}}$, and from \cref{repr_works_is_same} we know
$\worksc{A\cc B\cc C}{\sqs{S}}$.
\end{proof}

>>>>

\begin{mydef}[Sets of sequences]
As we will frequently refer to sets of fequences,
we will use calligraphic letters (e.g. $\sqs{A}$, $\sqs{B}$, $\sqs{C}$ and $\sqs{S}$)
to denote such sets for brevity.
We will use $A\cc\sqs{B}$ to denote the set of sequences $\{A\cc B\whr B\in\sqs{B}\}$,
and $\Dom{\sqs{A}}$ to denote $\bigcap_{A\in\sqs{A}} \Dom{A}$.
\end{mydef}

@@

\begin{mycor}\label{workschained}
% An inference rule in the algebra
$\worksmeqsign$ can be chained:
if $\sqs{B'}\subseteq\sqs{B}$, then
$\worksm{\sqs{A}}{\sqs{B}} \wedge \worksm{\sqs{B'}}{\sqs{C}} \Rightarrow \worksm{\sqs{A}}{\sqs{C}}$.
\end{mycor}

@@

\begin{mydef}[$\T$]
We use $\T$ and write $a\T$ to denote the canonical mapping of 
values, filesystems, commands and sequences to the
representatives of their $\typeeq$-equivalence class.
\begin{itemize}
\item For values, $\vald\T=\vald$, $\valf\T=\fil$ and $\empt\T=\empt$.
\item For filesystems, $\FS\T$ is defined by $\FS\T(n) = \FS(n)\T$.
\item For commands, $\cbrk\T=\cbrk$ and $\cxynv\T = \cTxynv$.
\item For sequences of commands, $\emptyseq\T=\emptyseq$, and if $S'=\alpha\cc S$, then $S'\T=\alpha\T\cc S\T$.
\item Finally we extend $\T$ to sets of sequences: $\sqs{A}\T = \{S\T \whr S\in\sqs{A}\}$.
\end{itemize}
\end{mydef}

@@

From the definitions we can clearly see that - TODO not used
\begin{mycor}\label{negneg_is_typeeq}
$\forall S: ({S\T}^{-1})^{-1} = S\T$.
\end{mycor}

@@

We use this result to prove the following:

\begin{mylem}\label{indep_prefix_combine}
The combination of sequences with a common head and independent tails 
continues to work under the same conditions:
\begin{gather*}
 \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
 \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
\end{gather*}
\end{mylem}
\begin{proof}
Based on \cref{repr_works_is_same} we have
$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
and from \cref{r_invmove} we know
$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
Using \cref{combine_independent_sequences} we get
$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
and chaining these using \cref{workschained}
we get
$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.

From $\worksmxb{\sqs{S}}{A\cc B}$ we also know $\worksmxb{\sqs{S}}{A}$ and $\worksmxb{\sqs{S}\T}{A\T}$.
We can combine this and $\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$ using
\cref{r_invmove} to get
$\worksmxb{\sqs{S}\T}{A\T\cc B\T\cc C\T}$, and from \cref{repr_works_is_same} we know
$\worksmxb{\sqs{S}}{A\cc B\cc C}$.
\end{proof}
